My Cool Title

### 2019-05-05 paper.tex
Removed a few todos

A complete system diagram is given in Fig.~\ref{fig:sys-diagram}\todo{cite own work where fig is from if necessary}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.

@@

In this case, the error is defined as the difference between the desired object and the object currently within view. 
The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}

>>>>

A complete system diagram is given in Fig.~\ref{fig:sys-diagram}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, but has been modified to incorporate a human within the loop.

@@

In this case, the error is defined as the difference between the desired object and the object currently within view. 
The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}
